Grad school is a perilous trail where many have helped me.

Much of the work contained here was contributed by coauthors and collaborators, notably Luis Ceze, Kaiyuan Zhang, Xi Wang, Karin Strauss, Tianqi Chen, Lianmin Zheng, and Yanping Huang in roughly chronological order.
I have been guided by the inexorable optimism of Luis, who amazingly is simultaneously the most senior and least cynical computer architect that I know.
Beyond Luis, I must thank all those whom aided me along the way.
My mentors in industry: Daniel Johnson and Mark Stephenson at NVIDIA and Yanping Huang at Google.

The sampanistas, especially those in my cohort: Meghan Cowan, Emily Furst, Ming Liu, and Liang Luo.
The $\blacksquare \blacksquare \blacksquare \blacksquare \blacksquare \blacksquare \blacksquare \blacksquare \blacksquare $, which includes Amrita Mazumdar and Luis Vega among those not already named.
The original bach$\blacksquare \blacksquare \blacksquare \blacksquare \blacksquare \blacksquare \blacksquare $-ers. %***************-ers.
The greater samp(l)(a) community.

Jeff Huang and Gifford Cheung, whose mentorship paved the way for my path to a PhD.
Mario Saenger, who had the patience to introduce a high school student to research.
My parents, who never questioned my journey despite having endured a much tougher time in grad school than I did.

Those in the illustrious twitch chats that I have frequented [gypsy9W, nyokenFace, jaeyunThink, terroruThumbsup, artoFace, x80smuXn00bmulLet, BlanderStrudel, x17steRobocopsagi, ClicksNCuts, justto5Think, salW, juggrW].
